Supplements for the manuscript `Variation in gaze following across the life span: A process-level perspective'

### 2024-04-17 supplements/supplements.Rmd
ready for revision

(ref:figlab1) **Comparison between models on a trial- or subject-level**. Grey dots show data of each trial. Solid lines show the mean predicted developmental trajectory for both models. Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level). 
```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
knitr::include_graphics("../figures/supplements_lifespan_modelstructure.pdf")
```

@@

| Diverse Beliefs | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Wellman et al., 1996 | Child sees a toy figure of a girl and a sheet of paper with bushes and a garage drawn on it. “Here’s Linda. Linda wants to find her cat. Her cat might be hiding in the bushes or it might be hiding in the garage. Where do you think the cat is? In the bushes or the garage?” This is the *own-belief* question., If the child chooses the bushes: “Well, that’s a good idea, but Linda thinks her cat is in the garage. She thinks her cat is in the garage.” (or vice versa) Then the child is asked the *target* question: “So where will Linda look for her cat? in the bushes or in the garage?”, To be correct, the child must answer the target question opposite from his/her answer to the *own-belief* question. | Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) |
| Knowledge Access | Wellman & Liu, 2004 → Pratt & Bryant (1990), Pillow (1989) | Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer. “Here’s a drawer. What do you think is inside the drawer?” (The child can give any answer she/he likes or indicate that she/he does not know). Next, the drawer is opened and the child is shown the content of the drawer: “Let’s see…it’s really a dog inside!” Close the drawer: “Okay, what is in the drawer?”, Then a toy figure of a girl is produced: “Polly has never ever seen inside this drawer. Now here comes Polly. So, does Polly know what is inside the drawer?” (*target* question) “Did Polly see inside this drawer?” (*memory* question”, To be correct, the child must answer the target question “no” and answer the memory control question “no”. | Toy figure of another girl, Plastic box with drawer, Toy dog |
| Contents False Belief | Wellman & Liu, 2004 → Perner, Leekam, & Wimmer, 1987; see also Wellman et al., 2001 | The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box. ‘‘Here’s a band-aid box. What do you think is inside the band-aid box?’’ Next, the band-aid box is opened: ‘‘Let’s see … it’s really a pig inside!’’ The band-aid box is closed: ‘‘Okay, what is in the band-aid box?’’ Then a toy figure of a boy is produced: ‘‘Peter has never ever seen inside this band-aid box. Now here comes Peter. So, what does Peter think is in the box? Band-Aids or a pig? (the *target* question) ‘‘Did Peter see inside this box?’’ (the *memory* question). To be correct the child must answer the target question ‘‘band-aids’’ and answer the memory question ‘‘no.’’ | Toy figure of a boy, Band-aid box , Toy pig |
| Explicit False Belief | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Siegal & Beattie, 1991 | Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it. ‘‘Here’s Scott. Scott wants to find his mittens. His mittens might be in his backpack or they might be in the closet. Really, Scott’s mittens are in his backpack. But Scott thinks his mittens are in the closet.’’ ‘‘So, where will Scott look for his mittens? In his backpack or in the closet?’’ (the *target* question) ‘‘Where are Scott’s mittens really? In his backpack or in the closet?’’ (the _reality_ question). To be correct the child must answer the target question ‘‘closet’’ and answer the reality question ‘‘backpack.’’ | Toy figure of another boy, Sheet of paper with a children’s room with a backpack and a clost on it |

>>>>

(ref:figlab1) **Comparison between models on a trial- or subject-level**. Grey dots show data of each trial. Solid lines show the mean predicted developmental trajectory for both models. Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).

```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
knitr::include_graphics(c("../figures/lifespan_plot.png"))
```

@@

| Diverse Beliefs | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Wellman et al., 1996 | Child sees a toy figure of a girl and a sheet of paper with bushes and a garage drawn on it. “Here’s Linda. Linda wants to find her cat. Her cat might be hiding in the bushes or it might be hiding in the garage. Where do you think the cat is? In the bushes or the garage?” This is the *own-belief* question., If the child chooses the bushes: “Well, that’s a good idea, but Linda thinks her cat is in the garage. She thinks her cat is in the garage.” (or vice versa) | Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden)
| | | Then the child is asked the *target* question: “So where will Linda look for her cat? in the bushes or in the garage?”, To be correct, the child must answer the target question opposite from his/her answer to the *own-belief* question. 
| Knowledge Access | Wellman & Liu, 2004 → Pratt & Bryant (1990), Pillow (1989) | Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer. “Here’s a drawer. What do you think is inside the drawer?” (The child can give any answer she/he likes or indicate that she/he does not know). Next, the drawer is opened and the child is shown the content of the drawer: “Let’s see…it’s really a dog inside!” Close the drawer: “Okay, what is in the drawer?”, Then a toy figure of a girl is produced: “Polly has never ever seen inside this drawer. | Toy figure of another girl, Plastic box with drawer, Toy dog |
| | | Now here comes Polly. So, does Polly know what is inside the drawer?” (*target* question) “Did Polly see inside this drawer?” (*memory* question”, To be correct, the child must answer the target question “no” and answer the memory control question “no”. 
| Contents False Belief | Wellman & Liu, 2004 → Perner, Leekam, & Wimmer, 1987; see also Wellman et al., 2001 | The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box. ‘‘Here’s a band-aid box. What do you think is inside the band-aid box?’’ Next, the band-aid box is opened: ‘‘Let’s see … it’s really a pig inside!’’ The band-aid box is closed: ‘‘Okay, what is in the band-aid box?’’ Then a toy figure of a boy is produced: ‘‘Peter has never ever seen inside this band-aid box. Now here comes Peter. So, what does Peter think is in the box? Band-Aids or a pig? (the *target* question) | Toy figure of a boy, Band-aid box , Toy pig |
| | | ‘‘Did Peter see inside this box?’’ (the *memory* question). To be correct the child must answer the target question ‘‘band-aids’’ and answer the memory question ‘‘no.’’ 
| Explicit False Belief | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Siegal & Beattie, 1991 | Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it. ‘‘Here’s Scott. Scott wants to find his mittens. His mittens might be in his backpack or they might be in the closet. Really, Scott’s mittens are in his backpack. But Scott thinks his mittens are in the closet.’’ ‘‘So, where will Scott look for his mittens? In his backpack or in the closet?’’ (the *target* question) ‘‘Where are Scott’s mittens really? In his backpack or in the closet?’’ (the _reality_ question). | Toy figure of another boy, Sheet of paper with a children’s room with a backpack and a clost on it |
| | | To be correct the child must answer the target question ‘‘closet’’ and answer the reality question ‘‘backpack.’’ 

### 2024-04-17 supplements/supplements.tex
ready for revision

{\centering \includegraphics[width=1\linewidth]{../figures/supplements_lifespan_modelstructure}

@@

Diverse Beliefs & Wellman \& Liu, 2004 → Wellman \& Bartsch, 1989; Wellman et al., 1996 & Child sees a toy figure of a girl and a sheet of paper with bushes and a garage drawn on it. ``Here's Linda. Linda wants to find her cat. Her cat might be hiding in the bushes or it might be hiding in the garage. Where do you think the cat is? In the bushes or the garage?'' This is the \emph{own-belief} question., If the child chooses the bushes: ``Well, that's a good idea, but Linda thinks her cat is in the garage. She thinks her cat is in the garage.'' (or vice versa) Then the child is asked the \emph{target} question: ``So where will Linda look for her cat? in the bushes or in the garage?'', To be correct, the child must answer the target question opposite from his/her answer to the \emph{own-belief} question. & Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) \\
Knowledge Access & Wellman \& Liu, 2004 → Pratt \& Bryant (1990), Pillow (1989) & Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer. ``Here's a drawer. What do you think is inside the drawer?'' (The child can give any answer she/he likes or indicate that she/he does not know). Next, the drawer is opened and the child is shown the content of the drawer: ``Let's see\ldots it's really a dog inside!'' Close the drawer: ``Okay, what is in the drawer?'', Then a toy figure of a girl is produced: ``Polly has never ever seen inside this drawer. Now here comes Polly. So, does Polly know what is inside the drawer?'' (\emph{target} question) ``Did Polly see inside this drawer?'' (\emph{memory} question'', To be correct, the child must answer the target question ``no'' and answer the memory control question ``no''. & Toy figure of another girl, Plastic box with drawer, Toy dog \\
Contents False Belief & Wellman \& Liu, 2004 → Perner, Leekam, \& Wimmer, 1987; see also Wellman et al., 2001 & The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box. ``Here's a band-aid box. What do you think is inside the band-aid box?'' Next, the band-aid box is opened: ``Let's see \ldots{} it's really a pig inside!'' The band-aid box is closed: ``Okay, what is in the band-aid box?'' Then a toy figure of a boy is produced: ``Peter has never ever seen inside this band-aid box. Now here comes Peter. So, what does Peter think is in the box? Band-Aids or a pig? (the \emph{target} question) `\,`Did Peter see inside this box?'' (the \emph{memory} question). To be correct the child must answer the target question ``band-aids'' and answer the memory question ``no.'' & Toy figure of a boy, Band-aid box , Toy pig \\
Explicit False Belief & Wellman \& Liu, 2004 → Wellman \& Bartsch, 1989; Siegal \& Beattie, 1991 & Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it. ``Here's Scott. Scott wants to find his mittens. His mittens might be in his backpack or they might be in the closet. Really, Scott's mittens are in his backpack. But Scott thinks his mittens are in the closet.'' ``So, where will Scott look for his mittens? In his backpack or in the closet?'' (the \emph{target} question) ``Where are Scott's mittens really? In his backpack or in the closet?'' (the \emph{reality} question). To be correct the child must answer the target question ``closet'' and answer the reality question ``backpack.'' & Toy figure of another boy, Sheet of paper with a children's room with a backpack and a clost on it \\

>>>>

{\centering \includegraphics[width=1\linewidth]{../figures/lifespan_plot}

@@

Diverse Beliefs & Wellman \& Liu, 2004 → Wellman \& Bartsch, 1989; Wellman et al., 1996 & Child sees a toy figure of a girl and a sheet of paper with bushes and a garage drawn on it. ``Here's Linda. Linda wants to find her cat. Her cat might be hiding in the bushes or it might be hiding in the garage. Where do you think the cat is? In the bushes or the garage?'' This is the \emph{own-belief} question., If the child chooses the bushes: ``Well, that's a good idea, but Linda thinks her cat is in the garage. She thinks her cat is in the garage.'' (or vice versa) & Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) \\
& & Then the child is asked the \emph{target} question: ``So where will Linda look for her cat? in the bushes or in the garage?'', To be correct, the child must answer the target question opposite from his/her answer to the \emph{own-belief} question. & \\
Knowledge Access & Wellman \& Liu, 2004 → Pratt \& Bryant (1990), Pillow (1989) & Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer. ``Here's a drawer. What do you think is inside the drawer?'' (The child can give any answer she/he likes or indicate that she/he does not know). Next, the drawer is opened and the child is shown the content of the drawer: ``Let's see\ldots it's really a dog inside!'' Close the drawer: ``Okay, what is in the drawer?'', Then a toy figure of a girl is produced: ``Polly has never ever seen inside this drawer. & Toy figure of another girl, Plastic box with drawer, Toy dog \\
& & Now here comes Polly. So, does Polly know what is inside the drawer?'' (\emph{target} question) ``Did Polly see inside this drawer?'' (\emph{memory} question'', To be correct, the child must answer the target question ``no'' and answer the memory control question ``no''. & \\
Contents False Belief & Wellman \& Liu, 2004 → Perner, Leekam, \& Wimmer, 1987; see also Wellman et al., 2001 & The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box. ``Here's a band-aid box. What do you think is inside the band-aid box?'' Next, the band-aid box is opened: ``Let's see \ldots{} it's really a pig inside!'' The band-aid box is closed: ``Okay, what is in the band-aid box?'' Then a toy figure of a boy is produced: '\,'Peter has never ever seen inside this band-aid box. Now here comes Peter. So, what does Peter think is in the box? Band-Aids or a pig? (the \emph{target} question) & Toy figure of a boy, Band-aid box , Toy pig \\
& & ``Did Peter see inside this box?'' (the \emph{memory} question). To be correct the child must answer the target question ``band-aids'' and answer the memory question ``no.'' & \\
Explicit False Belief & Wellman \& Liu, 2004 → Wellman \& Bartsch, 1989; Siegal \& Beattie, 1991 & Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it. ``Here's Scott. Scott wants to find his mittens. His mittens might be in his backpack or they might be in the closet. Really, Scott's mittens are in his backpack. But Scott thinks his mittens are in the closet.'' ``So, where will Scott look for his mittens? In his backpack or in the closet?'' (the \emph{target} question) ``Where are Scott's mittens really? In his backpack or in the closet?'' (the \emph{reality} question). & Toy figure of another boy, Sheet of paper with a children's room with a backpack and a clost on it \\
& & To be correct the child must answer the target question ``closet'' and answer the reality question ``backpack.'' & \\
